Overview

### 2021-05-27 overview_gh.Rmd
naive bayes support, merge #41 fix #43

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM` and seeded LDA models from `seededlda`.

@@

>>>>

`abstracts_stm` is an example topic model trained with the data `abstracts` using the `stm` package. Currently, this package supports structural topic models / correlated topic models from `stm`, Warp LDA models from `text2vec` , LDA/CTM models from `topicmodels`,  Biterm Topic Models from `BTM`, Keyword Assisted Topic Models from `keyATM`, and seeded LDA models from `seededlda`. Although not strictly a topic model, Naive Bayes models from `quanteda.textmodels` are also supported. See the section on [Naive Bayes](#about-naive-bayes) for more information.

@@

## About Naive Bayes

Naive Bayes model is a supervised machine learning model. This package supports Naive Bayes models trained using `quanteda.textmodels`.

Suppose `newsgroup_nb` is a Naive Bayes model trained on a subset of the classical [20 newgroups] dataset.

```r
tokens(newsgroup5$text, remove_punct = TRUE, remove_symbols = TRUE, remove_numbers = TRUE, remove_url = TRUE, spilit_hyphens = TRUE) %>% tokens_wordstem %>% tokens_remove(stopwords("en")) %>% dfm(tolower = TRUE) %>% dfm_trim(min_termfreq = 3, max_docfreq = 0.06, docfreq_type = "prop") -> newsgroup_dfm
docvars(newsgroup_dfm, "group") <- newsgroup5$title
newsgroup_nb <- textmodel_nb(newsgroup_dfm, docvars(newsgroup_dfm, "group"), distribution = "Bernoulli")
```

You can still generate word intrusion and word set intrusion tests.

```{r}
wi(newsgroup_nb)
```

```{r}
wsi(newsgroup_nb)
```
